---
title: "Inferential Data Analysis"
author: "Charles"
date: "August 7, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview
In this report we'll analyze the ToothGrowth data in the R datasets package and have a basic Inferential Data Analysis.

## Basic exploratory data analysis
Firstly we set up the environment:

```{r envir}
setwd("C:/Study/Coursera/1 Data-Science/2 RStudio/6 Class 6/Coursera_DataScience_Class6_FinalProject")
set.seed(135246987)
library(ggplot2)
library(gridExtra)
library(grid)
library(datasets)
```

Then we load the data and summarize the data:

```{r load data}
data("ToothGrowth")
dataTG <- ToothGrowth
str(dataTG)
head(dataTG)
summary(dataTG)
dataTG$dose <- as.factor(dataTG$dose)
```

We can get a general idea of the data according to explore above.
Then we can do some exploratory data analysis by drawing relationships between
length and supp & dose.

```{r exploPlot}
g1 <- ggplot(data = dataTG, aes(x=dose, y=len)) +
        geom_boxplot(aes(fill = dose))
g2 <- ggplot(data = dataTG, aes(x=supp ,y=len)) +
        geom_boxplot(aes(fill = supp))
grid.arrange(g1,g2,nrow=1)
```

As we can see above, it seems the length grows as dose increases.
While the replationship between length and supp is not quite obvious.

## T test for length and supp
We conduct t-test for length and supp:

```{r t len supp}
t.test(len ~ supp, data = dataTG, alternative ="two.sided")
```

As we can see above, $95 \%$ confidence interval contains zero and p-value is about
0.06.
So we wouldn't reject the null hypothesis, which means 
true difference in means is equal to 0.

## T test for length and dose.
We divide the data into three groups: dose in 0.5 and 1; dose in 0.5 and 2; dose in 1 and 2.

```{r divide}
dataTG_0.5_1.0 <- subset(dataTG, dose %in% c("0.5","1"))
dataTG_0.5_2.0 <- subset(dataTG, dose %in% c("0.5","2"))
dataTG_1.0_2.0 <- subset(dataTG, dose %in% c("1","2"))
```

Then do the t-test:

```{r t len dose}
t.test(len ~ dose, data = dataTG_0.5_1.0)
t.test(len ~ dose, data = dataTG_0.5_2.0)
t.test(len ~ dose, data = dataTG_1.0_2.0)
```

As we can see above, all three test the p-value is smaller than $5\%$ and the
$95 \%$ confidence interval dose not contain zero.
Besides, they are all negative, which means there's an increase as dose goes up.

## Conclusions and assumptions

According to the analysis above, we could see that under $95 \%$ confidence interval:

- Supplement has no effect on the length of tooth growth.
- Tooth grows longer as the dose increases.

Assumptions:

- The experiment was properly conducted.
- The sample data is good enough to represent the entire population.




































